---
title: "Dissertation Analysis"
output: html_document
date: "2024-04-11"
---

<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>


```{r set_up, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# read in the libraries
library(tidyverse) 
library(scales)
library(haven)
library(readxl)
library(gridExtra)
library(MatchIt)
library(missForest)
library(knitr)
library(ggplot2)
library(moments)
library(patchwork)
library(tmap)
library(sf)
library(tigris)

```

```{r functions}
# Function to standardize data types based on the first data frame
standardize_data_types <- function(df, first_df) {
  for (col_name in names(first_df)) {
    col_type <- typeof(first_df[[col_name]])
    if (col_type == "integer" || col_type == "numeric") {
      df[[col_name]] <- as.numeric(df[[col_name]])
    } else if (col_type == "character") {
      df[[col_name]] <- as.character(df[[col_name]])
    } else if (col_type == "logical") {
      df[[col_name]] <- as.logical(df[[col_name]])
    }
    # Add conditions for other data types if necessary
  }
  return(df)
}

transform_skewed_data <- function(data) {
  before_skewness <- c()  # Vector to store skewness values before transformation
  
  for (col in colnames(data)) {
    before_skewness <- c(before_skewness, moments::skewness(data[[col]]))  # Record skewness before transformation
    
    skewness_value <- moments::skewness(data[[col]])
    
    if (skewness_value > 1) {
      # Log transform for high positive skewness
      data[[col]] <- log(data[[col]] + 1)  # Adding 1 to avoid log(0)
    } else if (skewness_value < -1) {
      # Square root transform for high negative skewness
      data[[col]] <- sqrt(max(data[[col]] + 1) - data[[col]])
    } else if (skewness_value > 0.5) {
      # Square root transform for moderate positive skewness
      data[[col]] <- sqrt(data[[col]])
    } else if (skewness_value < -0.7) {
      # Square transform for moderate negative skewness
      data[[col]] <- (max(data[[col]]) - data[[col]])^2
    }
    
    # Standardize the data
    #data[[col]] <- scale(data[[col]])
  }
  
  after_skewness <- sapply(data, moments::skewness)  # Calculate skewness after transformation
  
  # Create a data frame to display skewness values before and after transformation
  skewness_table <- data.frame(
    Variable = colnames(data),
    Before_Transformation = before_skewness,
    After_Transformation = after_skewness
  )
  
  return(data)
}
```

## Data Sources

- **2020 BLM protest Data**
  - Accessed from The Armed Conflict Location & Event Data Project (ACLED)
- **Demographic County Data**
  - Characteristics
    - Percent Female
    - Age 0-18, 19-35, 36-50, 50-65, 65+
    - Percent Black, Asian, White, Hispanic or Latino
    - Person's 25 and older educational attainment
    - Median HH income
  - Accessed from IPUMS National Historical Geographic Information System (NHGIS) from the 2022 American Community Survey (ACS) Summary Files which estimates average characteristics from 2018 to 2022. 
- **Ideology Data**
  - Values are between 0 and 1, lower values are associated with politically left preferences and higher values with politically right preferences
  - Ideology is based on surveys taken between 2017-2021
  - Accessed from the Harvard Dataverse, dataset: Subnational ideology and presidential vote estimates (v2022)
- **Police Killings Data**
  - Average Police Killings Per Capita from 2016 - 2020
  - Accessed from mapping Police Violence


```{r get_protest_data, eval = FALSE}
# Get protest data
raw <- read.csv("data/2020-01-01-2024-04-19-United_States.csv")

blm_df <- raw %>%
  filter(year == 2020, 
         str_detect(tolower(assoc_actor_1), "blm")) %>%
  mutate(admin2 = ifelse(event_id_cnty %in% c("USA4796", "USA17359", 
                                              "USA12192", "USA9274", 
                                              "USA9021", "USA8471", "USA18357"), 
                         "new york", admin2),
         sub_event_type = ifelse(sub_event_type %in% c("Violent demonstration", 
                                                        "Mob violence",
                                                       "Protest with intervention",
                                                        "Excessive force against protesters"),
                                 "violent_protest", "peaceful_protest"),
         location = ifelse(location == "", NA, location),
         admin2 = ifelse(admin2 == "", NA, admin2),
         location = tolower(location),
         admin2 = tolower(admin2),
         admin1 = tolower(admin1),
         state_abbr = state.abb[match(admin1, tolower(state.name))],
         city_state = paste(location, state_abbr, sep = "_"),
         county_state = paste(admin2, state_abbr, sep = "_"))

cities_blm <- blm_df %>%
  group_by(city_state) %>%
  summarise(
    violent_protest = ifelse(any(sub_event_type == "violent_protest"), 1, 0),
    peaceful_protest = ifelse(all(sub_event_type == "peaceful_protest"), 1, 0)
  ) %>%
  mutate(is_city = 1) %>%
  rename(location = city_state)

counties_blm <- blm_df %>%
  group_by(county_state) %>%
  summarise(
    violent_protest = ifelse(any(sub_event_type == "violent_protest"), 1, 0),
    peaceful_protest = ifelse(all(sub_event_type == "peaceful_protest"), 1, 0)
  ) %>%
  mutate(is_city = 0) %>%
  rename(location = county_state)

blm <- rbind(cities_blm, counties_blm)

```

```{r get_political_data, eval = FALSE}
cities_pol_ideo <- read_dta("data/aip_cities_ideology_v2022a.dta")
counties_pol_ideo <- read_dta("data/aip_counties_ideology_v2022a.dta")
zips_pol_ideo <- read_dta("data/aip_zips_ideology_v2022a.dta")

cities_pol_ideo <- cities_pol_ideo %>%
  filter(survey_period == "2017-2021") %>% #Only use data from most recent surveys
  mutate(state_abbr = state.abb[match(state, state.name)], #get abbreviated states
         city_name = tolower(gsub(" County| Borough| Census Area| Municipality| Parish| city", "", city_name)), #remove suffixes
         city_state = paste(city_name, state_abbr, sep = "_")) %>% #combine county/states
  select(city_state, mrp_ideology)

counties_pol_ideo <- counties_pol_ideo %>%
  filter(survey_period == "2017-2021") %>% #Only use data from most recent surveys
  mutate(state_abbr = state.abb[match(state, state.name)], #get abbreviated states
         county_name = tolower(gsub(" County| Borough| Census Area| Municipality| Parish| city", "", county_name)), #remove suffixes
         county_state = paste(county_name, state_abbr, sep = "_")) %>% #combine county/states
  select(county_state, mrp_ideology)

duplicate_counties <- counties_pol_ideo  %>% 
  group_by(county_state) %>% 
  filter(n() > 1)

counties_pol_ideo <- counties_pol_ideo %>%
  group_by(county_state) %>%
  summarise(across(everything(), mean, na.rm = TRUE)) %>%
  ungroup()

zips_pol_ideo_by_name <- zips_pol_ideo %>%
  mutate(zip_name = str_replace(zip_name, ", ", "_"),
         zip_name = str_replace(zip_name, "([^_]+)(_.*)", function(x) {
    paste0(str_to_lower(sub("_.*", "", x)), sub("^[^_]+", "", x))
  })) %>%
  group_by(zip_name) %>%
  summarise(across(everything(), mean, na.rm = TRUE)) %>%
  ungroup() %>%
  select(zip_name, mrp_ideology) %>%
  rename(city_state = zip_name)

zips_pol_ideo_by_num <- zips_pol_ideo %>%
  group_by(zip) %>%
  summarise(across(everything(), mean, na.rm = TRUE)) %>%
  ungroup() %>%
  select(zip, mrp_ideology) %>%
  mutate(zip = as.character(zip))

```

```{r get_demographic_data, eval = FALSE}
cities_demo <- read.csv("data/nhgis0006_ts_nominal_place.csv")
counties_demo <- read.csv("data/nhgis0004_ts_nominal_county.csv")

cities_demo_df <- cities_demo %>%
  rename(total_pop = AV0AA225,
         num_female = AV1AB225,
         age_under_5 = B57AA225,
         age_5_9 = B57AB225,
         age_10_14 = B57AC225,
         age_15_17 = B57AD225,
         age_18_19 = B57AE225,
         age_20 = B57AF225,
         age_21 = B57AG225,
         age_22_24 = B57AH225,
         age_25_29 = B57AI225,
         age_30_34 = B57AJ225,
         age_35_44 = B57AK225,
         age_45_54 = B57AL225,
         age_55_59 = B57AM225,
         age_60_61 = B57AN225,
         age_62_64 = B57AO225,
         age_65_74 = B57AP225,
         age_75_84 = B57AQ225,
         age_85_up = B57AR225,
         num_black = B07AB225,
         num_white = B07AA225,
         num_asian = B07AD225,
         num_hispanic = A35AA225, 
         num_less_hs = B85AA225,
         num_hs_graduate_GED = B85AC225,
         num_associates = B85AE225,
         num_bachelors = B85AF225,
         num_graduate_professional = B85AG225,
         num_not_in_labor_force = B84AF225,
         median_hh_income = B79AA225
         )%>%
  mutate(percent_female = num_female / total_pop,
         perc_age_0_17 = (age_under_5 + 
                            age_5_9 + 
                            age_10_14 + 
                            age_15_17) / total_pop,
         perc_age_18_34 = (age_18_19 + 
                             age_20 + 
                             age_21 + 
                             age_22_24 + 
                             age_25_29 + 
                             age_30_34) / total_pop,
         perc_age_35_59 = (age_35_44 +
                             age_45_54 +
                             age_55_59) / total_pop,
         perc_age_60_74 = (age_60_61 +
                             age_62_64 +
                             age_65_74) / total_pop,
         perc_75_up = (age_75_84 +
                         age_85_up) / total_pop,
         perc_black = num_black / total_pop,
         perc_asian = num_asian / total_pop,
         perc_white = num_white / total_pop,
         perc_hispanic = num_hispanic / total_pop,
         perc_less_hs = num_less_hs / total_pop,
         perc_associates = num_associates / total_pop,
         perc_bachelors = num_bachelors / total_pop,
         perc_graduate_professional = num_graduate_professional / total_pop,
         perc_not_in_labor_force = num_not_in_labor_force / total_pop,
         state_abbr = state.abb[match(STATE, state.name)],
         PLACE = tolower(gsub(" County| Borough| Census Area| Municipality| Parish| city| town| CDP| village| City", "", PLACE)), #remove suffixes
         city_state = paste(PLACE, state_abbr, sep = "_") #combine county/states
         ) %>%
  select(city_state, percent_female, perc_age_0_17, perc_age_18_34, 
         perc_age_35_59, perc_age_60_74, perc_75_up, perc_black,
         perc_asian, perc_white, perc_hispanic, perc_less_hs, perc_associates,
         perc_bachelors, perc_graduate_professional, perc_not_in_labor_force,
         median_hh_income)

cities_processed <- cities_demo_df %>%
  group_by(city_state) %>%
  summarise(across(everything(), mean, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(is_city = 1) %>%
  rename(location = city_state)

counties_demo_df <- counties_demo %>%
  rename(total_pop = AV0AA225,
         num_female = AV1AB225,
         age_under_5 = B57AA225,
         age_5_9 = B57AB225,
         age_10_14 = B57AC225,
         age_15_17 = B57AD225,
         age_18_19 = B57AE225,
         age_20 = B57AF225,
         age_21 = B57AG225,
         age_22_24 = B57AH225,
         age_25_29 = B57AI225,
         age_30_34 = B57AJ225,
         age_35_44 = B57AK225,
         age_45_54 = B57AL225,
         age_55_59 = B57AM225,
         age_60_61 = B57AN225,
         age_62_64 = B57AO225,
         age_65_74 = B57AP225,
         age_75_84 = B57AQ225,
         age_85_up = B57AR225,
         num_black = B07AB225,
         num_white = B07AA225,
         num_asian = B07AD225,
         num_hispanic = A35AA225, 
         num_less_hs = B85AA225,
         num_hs_graduate_GED = B85AC225,
         num_associates = B85AE225,
         num_bachelors = B85AF225,
         num_graduate_professional = B85AG225,
         num_not_in_labor_force = B84AF225,
         median_hh_income = B79AA225
         ) %>%
  mutate(percent_female = num_female / total_pop,
         perc_age_0_17 = (age_under_5 + 
                            age_5_9 + 
                            age_10_14 + 
                            age_15_17) / total_pop,
         perc_age_18_34 = (age_18_19 + 
                             age_20 + 
                             age_21 + 
                             age_22_24 + 
                             age_25_29 + 
                             age_30_34) / total_pop,
         perc_age_35_59 = (age_35_44 +
                             age_45_54 +
                             age_55_59) / total_pop,
         perc_age_60_74 = (age_60_61 +
                             age_62_64 +
                             age_65_74) / total_pop,
         perc_75_up = (age_75_84 +
                         age_85_up) / total_pop,
         perc_black = num_black / total_pop,
         perc_asian = num_asian / total_pop,
         perc_white = num_white / total_pop,
         perc_hispanic = num_hispanic / total_pop,
         perc_less_hs = num_less_hs / total_pop,
         perc_associates = num_associates / total_pop,
         perc_bachelors = num_bachelors / total_pop,
         perc_graduate_professional = num_graduate_professional / total_pop,
         perc_not_in_labor_force = num_not_in_labor_force / total_pop,
         state_abbr = state.abb[match(STATE, state.name)],
         COUNTY = tolower(COUNTY) %>%
           gsub(" county| borough| census area| municipality| parish| city", "", .), # remove suffixes
         county_state = paste(COUNTY, state_abbr, sep = "_") # combine county/states
         ) %>%
  select(county_state, percent_female, perc_age_0_17, perc_age_18_34, 
         perc_age_35_59, perc_age_60_74, perc_75_up, perc_black,
         perc_asian, perc_white, perc_hispanic, perc_less_hs, perc_associates,
         perc_bachelors, perc_graduate_professional, perc_not_in_labor_force,
         median_hh_income)

counties_processed <- counties_demo_df %>%
  group_by(county_state) %>%
  summarise(across(everything(), mean, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(is_city = 0) %>%
  rename(location = county_state)

demographics <- rbind(counties_processed,cities_processed)

```

```{r get_police_killings, eval = FALSE}
police_killings_df <- read_excel("data/MPVDatasetDownload.xlsx", 
                                sheet = "2013-2024 Police Killings")

city_police_killings <- police_killings_df %>%
  filter(!is.na(City)) %>%
  mutate(`Date of Incident (month/day/year)` = as.Date(`Date of Incident (month/day/year)`),
         year = year(`Date of Incident (month/day/year)`),
         City = tolower(gsub(" County| Borough| Census Area| Municipality| Parish| city", "", City)),
         city_state = paste(tolower(City), State, sep = "_")) %>%
  filter(year >= 2016 & year <= 2020) %>%
  group_by(city_state) %>%
  summarize(count = n(), .groups = 'drop') %>%
  mutate(has_police_killing = ifelse(count > 0, 1, 0),
         is_city = 1) %>%
  select(city_state, has_police_killing, is_city) %>%
  rename(location = city_state)

county_police_killings <- police_killings_df %>%
  filter(!is.na(County)) %>%
  mutate(`Date of Incident (month/day/year)` = as.Date(`Date of Incident (month/day/year)`),
         year = year(`Date of Incident (month/day/year)`),
         County = tolower(gsub(" County| Borough| Census Area| Municipality| Parish| city", "", County)),
         county_state = paste(tolower(County), State, sep = "_")) %>%
  filter(year >= 2016 & year <= 2020) %>%
  group_by(county_state) %>%
  summarize(count = n(), .groups = 'drop') %>%
  mutate(has_police_killing = ifelse(count> 0, 1, 0),
         is_city = 0) %>%
  select(county_state, has_police_killing, is_city) %>%
  rename(location = county_state)

police_killings <- rbind(county_police_killings, city_police_killings)
```

```{r get_funding_data}
load(file='data/38651-0001-Data.rda')

police_df <- da38651.0001 %>%
  filter(AGENCYSAMPTYPE != "(5) State police") %>%
  mutate(
    CITY = str_trim(CITY, side = "both"),
    AGENCYNAME = str_trim(AGENCYNAME, side = "both"),
    AGENCYNAME = tolower(AGENCYNAME),
    City = tolower(CITY),
    County = ifelse(AGENCYSAMPTYPE == "(4) County police", 
                    str_extract(AGENCYNAME, ".*(?= county)"), NA),
    County = case_when(
       AGENCYNAME == "fraser winter park police department" ~ "grand",
       AGENCYNAME == "colonial regional police department" ~ "northampton",
       AGENCYNAME == "charleroi regional police department" ~ "washington",
       AGENCYNAME == "clear lake-ventura police department" ~ "calhoun",
       AGENCYNAME == "athens clarke county police department" ~ "clarke",
       AGENCYNAME == "saint charles county police department" ~ "st. charles",
       AGENCYNAME == "saint louis county police department" ~ "st. louis",
       AGENCYNAME == "bath police department" & STATE == "ME" ~ "sagadahoc",
      AGENCYNAME == "somers town police department" ~ "westchester",
      AGENCYNAME == "little river - academy police department" ~ "bell",
      AGENCYNAME == "linn town police department" ~ "walworth",
      AGENCYNAME == "hot springs police department" ~ "garland",
      AGENCYNAME == "ventura police department buenaventura" ~ "ventura",
      AGENCYNAME == "west sacramento police department" ~ "yolo",
      AGENCYNAME == "miramar police department" ~ "broward",
      AGENCYNAME == "honolulu police department" ~ "honolulu",
      AGENCYNAME == "mcleansboro police department" ~ "hamilton",
      AGENCYNAME == "round lake park police department" ~ "lake",
      AGENCYNAME == "lasalle police department" ~ "cook",
      AGENCYNAME == "mount pulaski police department" ~ "logan",
      AGENCYNAME == "laporte police department" ~ "laporte",
      AGENCYNAME == "indianapolis metro police department" ~ "marion",
      AGENCYNAME == "lexington division of police" ~ "fayette",
      AGENCYNAME == "louisville metro police department" ~ "jefferson",
      AGENCYNAME == "barnstable police department" ~ "barnstable",
      AGENCYNAME == "dighton police department" ~ "bristol",
      AGENCYNAME == "seekonk police department" ~ "bristol",
      AGENCYNAME == "west tisbury police department" ~ "dukes",
      AGENCYNAME == "groveland police department" ~ "essex",
      AGENCYNAME == "methuen police department" ~ "essex",
      AGENCYNAME == "ashfield police department" ~ "franklin",
      AGENCYNAME == "west springfield police department" ~ "hampden",
      AGENCYNAME == "southampton police department" ~ "hampshire",
      AGENCYNAME == "littleton police department" ~ "middlesex",
      AGENCYNAME == "tyngsboro police department" ~ "middlesex",
      AGENCYNAME == "foxboro police department" ~ "norfolk",
      AGENCYNAME == "carver police department" ~ "plymouth",
      AGENCYNAME == "blackstone police department" ~ "worcester",
      AGENCYNAME == "hardwick police department" ~ "worcester",
      AGENCYNAME == "holden police department" ~ "worcester",
      AGENCYNAME == "southbridge police department" ~ "worcester",
      AGENCYNAME == "westminster police department" ~ "worcester",
      AGENCYNAME == "st michaels police" ~ "talbot",
      AGENCYNAME == "baileyville police department" ~ "washington",
      AGENCYNAME == "buxton police department" ~ "york",
      AGENCYNAME == "huron township police department" ~ "wayne",
      AGENCYNAME == "brownstown township police department" ~ "wayne",
      AGENCYNAME == "lees summit police department" ~ "jackson",
      AGENCYNAME == "city of o'fallon mo police department" ~ "st. charles",
      AGENCYNAME == "ste genevieve police department" ~ "ste. genevieve",
      AGENCYNAME == "winston-salem police department" ~ "forsyth",
      AGENCYNAME == "whispering pines police department" ~ "moore",
      AGENCYNAME == "center harbor police department" ~ "belknap",
      AGENCYNAME == "tuftonboro police department" ~ "carroll",
      AGENCYNAME == "harrisville police department" ~ "cheshire",
      AGENCYNAME == "carroll police department" ~ "coos",
      AGENCYNAME == "pelham police department" ~ "hillsborough",
      AGENCYNAME == "bow police department" ~ "merrimack",
      AGENCYNAME == "auburn police department" ~ "rockingham",
      AGENCYNAME == "east kingston police department" ~ "rockingham",
      AGENCYNAME == "nottingham police department" ~ "rockingham",
      AGENCYNAME == "lee police department" ~ "strafford",
      AGENCYNAME == "edgewater police" ~ "bergen",
      AGENCYNAME == "ho-ho-kus police" ~ "bergen",
      AGENCYNAME == "montvale police" ~ "bergen",
      AGENCYNAME == "norwood police" ~ "bergen",
      AGENCYNAME == "river vale police" ~ "bergen",
      AGENCYNAME == "wallington police department" ~ "bergen",
      AGENCYNAME == "woodcliff lake police" ~ "bergen",
      AGENCYNAME == "riverside township police" ~ "burlington",
      AGENCYNAME == "cherry hill police" ~ "camden",
      AGENCYNAME == "haddon heights police" ~ "camden",
      AGENCYNAME == "mount ephraim police" ~ "camden",
      AGENCYNAME == "pine valley police" ~ "camden",
      AGENCYNAME == "runnemede police" ~ "camden",
      AGENCYNAME == "avalon police department" ~ "cape may",
      AGENCYNAME == "belleville police" ~ "essex",
      AGENCYNAME == "bloomfield police" ~ "essex",
      AGENCYNAME == "cedar grove township police" ~ "essex",
      AGENCYNAME == "irvington police" ~ "essex",
      AGENCYNAME == "montclair police" ~ "essex",
      AGENCYNAME == "orange police" ~ "essex",
      AGENCYNAME == "verona police" ~ "essex",
      AGENCYNAME == "north bergen police" ~ "hudson",
      AGENCYNAME == "weehawken police" ~ "hudson",
      AGENCYNAME == "tewksbury township police" ~ "hunterdon",
      AGENCYNAME == "hamilton township police department" ~ "mercer",
      AGENCYNAME == "edison police" ~ "middlesex",
      AGENCYNAME == "atlantic highlands police" ~ "monmouth",
      AGENCYNAME == "neptune city police" ~ "monmouth",
      AGENCYNAME == "hazlet township police department" ~ "monmouth",
      AGENCYNAME == "riverdale police" ~ "morris",
      AGENCYNAME == "beachwood police" ~ "ocean",
      AGENCYNAME == "jackson township police" ~ "ocean",
      AGENCYNAME == "lavallette police" ~ "ocean",
      AGENCYNAME == "little egg harbor township police" ~ "ocean",
      AGENCYNAME == "point pleasant borough police" ~ "ocean",
      AGENCYNAME == "seaside heights police" ~ "ocean",
      AGENCYNAME == "prospect park police" ~ "passaic",
      AGENCYNAME == "wayne township police" ~ "passaic",
      AGENCYNAME == "west milford township police" ~ "passaic",
      AGENCYNAME == "far hills police" ~ "somerset",
      AGENCYNAME == "ogdensburg police" ~ "sussex",
      AGENCYNAME == "stanhope police" ~ "sussex",
      AGENCYNAME == "vernon township police" ~ "sussex",
      AGENCYNAME == "clark police department" ~ "union",
      AGENCYNAME == "winfield police" ~ "union",
      AGENCYNAME == "washington township police" ~ "warren",
      AGENCYNAME == "amherst town police department" ~ "erie",
      AGENCYNAME == "town of windham police department" ~ "greene",
      AGENCYNAME == "kent town police department" ~ "putnam",
      AGENCYNAME == "pound ridge town police department" ~ "westchester",
      AGENCYNAME == "west chester police department" ~ "hamilton",
      AGENCYNAME == "orange village police department" ~ "cuyahoga",
      AGENCYNAME == "fowler township police department" ~ "trumbull",
      AGENCYNAME == "hamilton township police department" ~ "warren",
      AGENCYNAME == "cumberland township police department" ~ "adams",
      AGENCYNAME == "mckees rocks borough police department" ~ "allegheny",
      AGENCYNAME == "south park township police department" ~ "allegheny",
      AGENCYNAME == "parks township police department" ~ "armstrong",
      AGENCYNAME == "rochester township police department" ~ "beaver",
      AGENCYNAME == "douglass township police department" ~ "berks",
      AGENCYNAME == "warminster township police department" ~ "bucks",
      AGENCYNAME == "buckingham township police department" ~ "bucks",
      AGENCYNAME == "east conemaugh borough police department" ~ "cambria",
      AGENCYNAME == "patton township police department" ~ "centre",
      AGENCYNAME == "upper uwchlan township police department" ~ "chester",
      AGENCYNAME == "west vincent township police department" ~ "chester",
      AGENCYNAME == "upper allen township police department" ~ "cumberland",
      AGENCYNAME == "darby township police department" ~ "delaware",
      AGENCYNAME == "upper darby township police department" ~ "delaware",
      AGENCYNAME == "upper providence township police department" ~ "delaware",
      AGENCYNAME == "scott township police department" ~ "lackawanna",
      AGENCYNAME == "ephrata police department" ~ "lancaster",
      AGENCYNAME == "union township police department" ~ "lawrence",
      AGENCYNAME == "courtdale borough police department" ~ "luzerne",
      AGENCYNAME == "grove city police department" ~ "mercer",
      AGENCYNAME == "granville township police department" ~ "mifflin",
      AGENCYNAME == "east norriton township police department" ~ "montgomery",
      AGENCYNAME == "lower pottsgrove township police department" ~ "montgomery",
      AGENCYNAME == "lower frederick township police department" ~ "montgomery",
      AGENCYNAME == "limerick township police department" ~ "montgomery",
      AGENCYNAME == "upper nazareth township police department" ~ "northampton",
      AGENCYNAME == "rush township police department" ~ "schuylkill",
      AGENCYNAME == "cecil township police department" ~ "washington",
      AGENCYNAME == "allegheny township police department" ~ "westmoreland",
      AGENCYNAME == "lower windsor township police department" ~ "york",
      AGENCYNAME == "west warwick police" ~ "kent",
      AGENCYNAME == "north smithfield police" ~ "providence",
      AGENCYNAME == "north kingstown police" ~ "washington",
      AGENCYNAME == "south kingstown police" ~ "washington",
      AGENCYNAME == "new shoreham police" ~ "washington",
      AGENCYNAME == "mccormick police department" ~ "mccormick",
      AGENCYNAME == "metro nashville police department" ~ "davidson",
      AGENCYNAME == "rutland town police department" ~ "rutland",
    AGENCYNAME == "somers town police department" ~ "westchester",
    AGENCYNAME == "little river - academy police department" ~ "bell",
    AGENCYNAME == "linn town police department" ~ "walworth",
    AGENCYNAME == "hot springs police department" ~ "garland",
    AGENCYNAME == "ventura police department buenaventura" ~ "ventura",
    AGENCYNAME == "west sacramento police department" ~ "yolo",
    AGENCYNAME == "metropolitan police department - dc" ~ "district of columbia",
    AGENCYNAME == "miramar police department" ~ "broward",
    AGENCYNAME == "honolulu police department" ~ "honolulu",
    AGENCYNAME == "mcleansboro police department" ~ "hamilton",
    AGENCYNAME == "round lake park police department" ~ "lake",
    AGENCYNAME == "lasalle police department" ~ "la salle",
    AGENCYNAME == "mount pulaski police department" ~ "logan",
    AGENCYNAME == "laporte police department" ~ "laporte",
    AGENCYNAME == "indianapolis metro police department" ~ "marion",
    AGENCYNAME == "lexington division of police" ~ "fayette",
    AGENCYNAME == "louisville metro police department" ~ "jefferson",
    AGENCYNAME == "barnstable police department" ~ "barnstable",
    AGENCYNAME == "dighton police department" ~ "bristol",
    AGENCYNAME == "seekonk police department" ~ "bristol",
    AGENCYNAME == "west tisbury police department" ~ "dukes",
    AGENCYNAME == "groveland police department" ~ "essex",
    AGENCYNAME == "methuen police department" ~ "essex",
    AGENCYNAME == "ashfield police department" ~ "franklin",
    AGENCYNAME == "west springfield police department" ~ "hampden",
    AGENCYNAME == "southampton police department" ~ "hampshire",
    AGENCYNAME == "littleton police department" ~ "middlesex",
    AGENCYNAME == "tyngsboro police department" ~ "middlesex",
    AGENCYNAME == "foxboro police department" ~ "norfolk",
    AGENCYNAME == "carver police department" ~ "plymouth",
    AGENCYNAME == "blackstone police department" ~ "worcester",
    AGENCYNAME == "hardwick police department" ~ "worcester",
    AGENCYNAME == "holden police department" ~ "worcester",
    AGENCYNAME == "southbridge police department" ~ "worcester",
    AGENCYNAME == "westminster police department" ~ "worcester",
    AGENCYNAME == "st michaels police" ~ "talbot",
    AGENCYNAME == "baileyville police department" ~ "washington",
    AGENCYNAME == "buxton police department" ~ "york",
    AGENCYNAME == "huron township police department" ~ "wayne",
    AGENCYNAME == "brownstown township police department" ~ "wayne",
    AGENCYNAME == "lees summit police department" ~ "jackson",
    AGENCYNAME == "city of o'fallon mo police department" ~ "st. charles",
    AGENCYNAME == "ste genevieve police department" ~ "ste. genevieve",
    AGENCYNAME == "winston-salem police department" ~ "forsyth",
    AGENCYNAME == "whispering pines police department" ~ "moore",
    AGENCYNAME == "center harbor police department" ~ "belknap",
    AGENCYNAME == "tuftonboro police department" ~ "carroll",
    AGENCYNAME == "harrisville police department" ~ "cheshire",
    AGENCYNAME == "carroll police department" ~ "coos",
    AGENCYNAME == "pelham police department" ~ "hillsborough",
    AGENCYNAME == "bow police department" ~ "merrimack",
    AGENCYNAME == "auburn police department" ~ "rockingham",
    AGENCYNAME == "east kingston police department" ~ "rockingham",
    AGENCYNAME == "nottingham police department" ~ "rockingham",
    AGENCYNAME == "lee police department" ~ "strafford",
    AGENCYNAME == "edgewater police" ~ "bergen",
    AGENCYNAME == "ho-ho-kus police" ~ "bergen",
    AGENCYNAME == "montvale police" ~ "bergen",
    AGENCYNAME == "norwood police" ~ "bergen",
    AGENCYNAME == "river vale police" ~ "bergen",
    AGENCYNAME == "wallington police department" ~ "bergen",
    AGENCYNAME == "woodcliff lake police" ~ "bergen",
    AGENCYNAME == "riverside township police" ~ "burlington",
    AGENCYNAME == "cherry hill police" ~ "camden",
    AGENCYNAME == "haddon heights police" ~ "camden",
    AGENCYNAME == "mount ephraim police" ~ "camden",
    AGENCYNAME == "pine valley police" ~ "camden",
    AGENCYNAME == "runnemede police" ~ "camden",
    AGENCYNAME == "avalon police department" ~ "cape may",
    AGENCYNAME == "belleville police" ~ "essex",
    AGENCYNAME == "bloomfield police" ~ "essex",
    AGENCYNAME == "cedar grove township police" ~ "essex",
    AGENCYNAME == "irvington police" ~ "essex",
    AGENCYNAME == "montclair police" ~ "essex",
    AGENCYNAME == "orange police" ~ "essex",
    AGENCYNAME == "verona police" ~ "essex",
    AGENCYNAME == "north bergen police" ~ "hudson",
    AGENCYNAME == "weehawken police" ~ "hudson",
    AGENCYNAME == "tewksbury township police" ~ "hunterdon",
    AGENCYNAME == "hamilton township police department" ~ "mercer",
    AGENCYNAME == "edison police" ~ "middlesex",
    AGENCYNAME == "atlantic highlands police" ~ "monmouth",
    AGENCYNAME == "neptune city police" ~ "monmouth",
    AGENCYNAME == "hazlet township police department" ~ "monmouth",
    AGENCYNAME == "riverdale police" ~ "morris",
    AGENCYNAME == "beachwood police" ~ "ocean",
    AGENCYNAME == "jackson township police" ~ "ocean",
    AGENCYNAME == "lavallette police" ~ "ocean",
    AGENCYNAME == "little egg harbor township police" ~ "ocean",
    AGENCYNAME == "point pleasant borough police" ~ "ocean",
    AGENCYNAME == "seaside heights police" ~ "ocean",
    AGENCYNAME == "prospect park police" ~ "passaic",
    AGENCYNAME == "wayne township police" ~ "passaic",
    AGENCYNAME == "west milford township police" ~ "passaic",
    AGENCYNAME == "far hills police" ~ "somerset",
    AGENCYNAME == "ogdensburg police" ~ "sussex",
    AGENCYNAME == "stanhope police" ~ "sussex",
    AGENCYNAME == "vernon township police" ~ "sussex",
    AGENCYNAME == "clark police department" ~ "union",
    AGENCYNAME == "winfield police" ~ "union",
    AGENCYNAME == "washington township police" ~ "warren",
    AGENCYNAME == "amherst town police department" ~ "erie",
    AGENCYNAME == "town of windham police department" ~ "greene",
    AGENCYNAME == "kent town police department" ~ "putnam",
    AGENCYNAME == "pound ridge town police department" ~ "westchester",
    AGENCYNAME == "west chester police department" ~ "butler",
    AGENCYNAME == "orange village police department" ~ "cuyahoga",
    AGENCYNAME == "fowler township police department" ~ "trumbull",
    AGENCYNAME == "hamilton township police department" ~ "warren",
    AGENCYNAME == "cumberland township police department" ~ "adams",
    AGENCYNAME == "mckees rocks borough police department" ~ "allegheny",
    AGENCYNAME == "south park township police department" ~ "allegheny",
    AGENCYNAME == "parks township police department" ~ "armstrong",
    AGENCYNAME == "rochester township police department" ~ "beaver",
    AGENCYNAME == "douglass township police department" ~ "berks",
    AGENCYNAME == "warminster township police department" ~ "bucks",
    AGENCYNAME == "buckingham township police department" ~ "bucks",
    AGENCYNAME == "east conemaugh borough police department" ~ "cambria",
    AGENCYNAME == "patton township police department" ~ "centre",
    AGENCYNAME == "upper uwchlan township police department" ~ "chester",
    AGENCYNAME == "west vincent township police department" ~ "chester",
    AGENCYNAME == "upper allen township police department" ~ "cumberland",
    AGENCYNAME == "darby township police department" ~ "delaware",
    AGENCYNAME == "upper darby township police department" ~ "delaware",
    AGENCYNAME == "upper providence township police department" ~ "delaware",
    AGENCYNAME == "scott township police department" ~ "lackawanna",
    AGENCYNAME == "ephrata police department" ~ "lancaster",
    AGENCYNAME == "union township police department" ~ "lawrence",
    AGENCYNAME == "courtdale borough police department" ~ "luzerne",
    AGENCYNAME == "grove city police department" ~ "mercer",
    AGENCYNAME == "granville township police department" ~ "mifflin",
    AGENCYNAME == "east norriton township police department" ~ "montgomery",
    AGENCYNAME == "lower pottsgrove township police department" ~ "montgomery",
    AGENCYNAME == "lower frederick township police department" ~ "montgomery",
    AGENCYNAME == "limerick township police department" ~ "montgomery",
    AGENCYNAME == "upper nazareth township police department" ~ "northampton",
    AGENCYNAME == "rush township police department" ~ "schuylkill",
    AGENCYNAME == "cecil township police department" ~ "washington",
    AGENCYNAME == "allegheny township police department" ~ "westmoreland",
    AGENCYNAME == "lower windsor township police department" ~ "york",
    AGENCYNAME == "west warwick police" ~ "kent",
    AGENCYNAME == "north smithfield police" ~ "providence",
    AGENCYNAME == "north kingstown police" ~ "washington",
    AGENCYNAME == "south kingstown police" ~ "washington",
    AGENCYNAME == "new shoreham police" ~ "washington",
    AGENCYNAME == "mccormick police department" ~ "mccormick",
    AGENCYNAME == "metro nashville police department" ~ "davidson",
    AGENCYNAME == "rutland town police department" ~ "rutland",
    AGENCYNAME == "bath police department" & STATE == "NH" ~ "grafton",
    AGENCYNAME == "brookline police department" & STATE == "NH"~ "hillsborough",
    AGENCYNAME == "canton police department" & STATE == "MA"~ "norfolk",
    AGENCYNAME == "newton police department" & STATE == "NH"~ "rockingham",
    TRUE ~ County),
    STATE = case_when(
      AGENCYNAME == "metropolitan police department - dc" ~ "NA",
      TRUE ~ STATE),
    City = str_replace(City, " city$", ""),
    City = if_else(str_detect(AGENCYNAME, "borough") & 
                     !str_detect(City, "pittsburgh") &
                     !str_detect(City, "king salmon") &
                     !str_detect(City, "marlborough") &
                     !str_detect(City, "gloucester") &
                     !str_detect(City, "point pleasant boro") &
                     !str_detect(City, "mc kees rocks") &
                     !str_detect(City, "conemaugh") &
                     !str_detect(City, "johnstown") &
                     !str_detect(City, "erie") &
                     !str_detect(City, "wilkes barre") &
                     !str_detect(City, "jonesborough"), 
                   paste(City, "borough"), 
                   City),
    City = if_else(str_detect(City, "saint"),str_replace(City, "saint", "st."), City),
    City = if_else(str_detect(City, "\\bn\\b"), str_replace(City, "\\bn\\b", "north"), City),
    City = if_else(str_detect(City, "\\bs\\b"), str_replace(City, "\\bs\\b", "south"), City),
    City = case_when(
      AGENCYNAME == "old saybrook police services" ~ "old saybrook center",
      AGENCYNAME == "stratford police department" ~ "stratford downtown",
      AGENCYNAME == "bedford police department" & STATE == "PA" ~ "coaldale borough (bedford)",
      AGENCYNAME == "brookline police department" & STATE == "PA"~ "coaldale borough (bedford)",
      AGENCYNAME == "cheshire police department" ~ "cheshire village",
      AGENCYNAME == "east windsor police department" ~ "hartford",
      AGENCYNAME == "farmington police department" & STATE == "CT" ~ "hartford",
      AGENCYNAME == "hamden police department" ~ "new haven",
      AGENCYNAME == "middlebury police department" ~ "new haven",
      AGENCYNAME == "madison police department" & STATE == "CT" ~ "madison center",
      AGENCYNAME == "winthrop police department" & STATE == "MA" ~ "winthrop town",
      AGENCYNAME == "westport police department" & STATE == "CT" ~ "westport village",
      AGENCYNAME == "fairfield police department" & STATE == "CT" ~ "long hill (fairfield)",
      AGENCYNAME == "walker county sheriff's department" ~ "lafayette",
      AGENCYNAME == "avon police department" & STATE == "MA" ~ "holbrook",
      AGENCYNAME == "ventura county sheriff's office" ~ "san buenaventura (ventura)",
      AGENCYNAME == "bibb county sheriff's office" ~ "macon-bibb",
      AGENCYNAME == "douglas county sheriff's office" & STATE == "GA" ~ "douglasville",
      AGENCYNAME == "milford police department" & STATE == "CT" ~ "milford (balance)",
      AGENCYNAME == "el paso county sheriff's office" & STATE == "CO" ~ "colorado springs",
      AGENCYNAME == "st john the baptist parish sheriff's office" ~ "laplace",
      AGENCYNAME == "spotsylvania county sheriff's office" ~ "spotsylvania courthouse",
      AGENCYNAME == "somerset county sheriff's office" & STATE == "NJ" ~ "somerville borough",
      AGENCYNAME == "saint johns county sheriff's office" & STATE == "FL" ~ "st. augustine",
      AGENCYNAME == "jackson county sheriff's office" & STATE == "MO" ~ "lee's summit",
      AGENCYNAME == "bedford police department" & STATE == "NH" ~ "manchester",
      AGENCYNAME == "florence county sheriff's office" & STATE == "SC" ~ "florence",
      AGENCYNAME == "prospect police department" & STATE == "CT" ~ "naugatuck borough",
      AGENCYNAME == "franklin police department" & STATE == "MA" ~ "franklin town",
      AGENCYNAME == "harvard police department" & STATE == "MA" ~ "cambridge",
      AGENCYNAME == "forsyth county sheriff's office" & STATE == "NC" ~ "winston-salem",
      AGENCYNAME == "greenville police department" & STATE == "PA" ~ "greenville borough",
      AGENCYNAME == "fontana police department" & STATE == "WI" ~ "fontana-on-geneva lake",
      AGENCYNAME == "hillsborough county sheriff's office" & STATE == "FL" ~ "tampa",
      AGENCYNAME == "jefferson county sheriff's office" & STATE == "KY" ~ "west louisville",
      AGENCYNAME == "ottawa county sheriff's office" & STATE == "MI" ~ "grand rapids",
      AGENCYNAME == "richmond county sheriff's office" & STATE == "GA" ~ "augusta-richmond consolidated government (balance)",
      AGENCYNAME == "rio arriba county sheriff's office" & STATE == "NM" ~ "española",
      AGENCYNAME == "stafford county sheriff's office" & STATE == "VA" ~ "stafford courthouse",
      TRUE ~ City
    ),
    ZIP = case_when(
        str_detect(AGENCYNAME, "stoneboro borough police department") ~ "16153",
        str_detect(AGENCYNAME, "china grove police department") ~ "28023",
        str_detect(AGENCYNAME, "la porte city police department") ~ "50651",
        str_detect(AGENCYNAME, "university heights police department") ~ "52246",
        str_detect(AGENCYNAME, "spaulding police department") ~ "62561",
        str_detect(AGENCYNAME, "advance police department") ~ "63730",
        str_detect(AGENCYNAME, "henderson police department") ~ "71334",
        str_detect(AGENCYNAME, "lake shore police department") ~ "56311",
        str_detect(AGENCYNAME, "custer city police department") ~ "73639",
        str_detect(AGENCYNAME, "fairview police department") ~ "75069",
        str_detect(AGENCYNAME, "clear lake shores police department") ~ "77565",
        str_detect(AGENCYNAME, "east tawakoni police department") ~ "75472",
        str_detect(AGENCYNAME, "brighton police department") ~ "35020",
        str_detect(AGENCYNAME, "frisco city police department") ~ "36445",
        str_detect(AGENCYNAME, "phenix city police department") ~ "36867",
        str_detect(AGENCYNAME, "pell city police department") ~ "35125",
        str_detect(AGENCYNAME, "cave city police department") ~ "72521",
        str_detect(AGENCYNAME, "johnson police department") ~ "72704",
        str_detect(AGENCYNAME, "union city police department") ~ "94587",
        str_detect(AGENCYNAME, "kensington police department") ~ "94707",
        str_detect(AGENCYNAME, "culver city police department") ~ "90232",
        str_detect(AGENCYNAME, "belvedere police department") ~ "94920",
        str_detect(AGENCYNAME, "daly city police department") ~ "94015",
        str_detect(AGENCYNAME, "commerce city police department") ~ "80022",
        str_detect(AGENCYNAME, "black hawk police department") ~ "80422",
        str_detect(AGENCYNAME, "lochbuie police department") ~ "80603",
        str_detect(AGENCYNAME, "cheshire police department") ~ "6410",
        str_detect(AGENCYNAME, "fairfield police department") & STATE == "CT" ~ "6096",
        str_detect(AGENCYNAME, "madison police department") & STATE == "CT" ~ "6443",
        str_detect(AGENCYNAME, "old saybrook police services") & STATE =="CT"~ "6475",
        str_detect(AGENCYNAME, "stratford police department") ~ "6615",
        str_detect(AGENCYNAME, "westport police department") ~ "6880",
        str_detect(AGENCYNAME, "delaware city police department") ~ "19706",
        str_detect(AGENCYNAME, "panama city police department") ~ "32401",
        str_detect(AGENCYNAME, "euharlee police department") ~ "30145",
        str_detect(AGENCYNAME, "mountain city police department GA") ~ "30562",
        str_detect(AGENCYNAME, "saint ansgar police department") ~ "50472",
        str_detect(AGENCYNAME, "sioux city police department") ~ "51101",
        str_detect(AGENCYNAME, "sauk village police department") ~ "60411",
        str_detect(AGENCYNAME, "indian head park police department") ~ "60525",
        str_detect(AGENCYNAME, "northfield police department") ~ "60093",
        str_detect(AGENCYNAME, "north riverside police department") ~ "60546",
        str_detect(AGENCYNAME, "east dundee police department") ~ "60118",
        str_detect(AGENCYNAME, "kildeer police department") ~ "60047",
        str_detect(AGENCYNAME, "prairie grove police department") ~ "60050",
        str_detect(AGENCYNAME, "greendale police department") ~ "47240",
        str_detect(AGENCYNAME, "long beach police department") ~ "46360",
        str_detect(AGENCYNAME, "tell city police department") ~ "47586",
        str_detect(AGENCYNAME, "dodge city police department") ~ "67801",
        str_detect(AGENCYNAME, "scott city police department") ~ "67871",
        str_detect(AGENCYNAME, "kansas city police department") ~ "66101",
        str_detect(AGENCYNAME, "edwardsville police department") ~ "66111",
        str_detect(AGENCYNAME, "bossier city police department") ~ "71111",
        str_detect(AGENCYNAME, "cottage city police") ~ "20722",
        str_detect(AGENCYNAME, "landover hills police") ~ "20784",
        str_detect(AGENCYNAME, "ocean city police") ~ "21842",
        str_detect(AGENCYNAME, "laurium police department") ~ "49913",
        str_detect(AGENCYNAME, "lake angelus police department") ~ "48326",
        str_detect(AGENCYNAME, "reed city police department") ~ "49677",
        str_detect(AGENCYNAME, "rockwood police department") ~ "48173",
        str_detect(AGENCYNAME, "lake tapawingo police department") ~ "64015",
        str_detect(AGENCYNAME, "montgomery city police department") ~ "63361",
        str_detect(AGENCYNAME, "platte woods police department") ~ "64151",
        str_detect(AGENCYNAME, "calverton park police department") ~ "63135",
        str_detect(AGENCYNAME, "frontenac police department") ~ "63131",
        str_detect(AGENCYNAME, "kansas city police department") ~ "64106",
        str_detect(AGENCYNAME, "central city police department") ~ "68826",
        str_detect(AGENCYNAME, "falls city police department") ~ "68355",
        str_detect(AGENCYNAME, "cape carteret police department") ~ "28584",
        str_detect(AGENCYNAME, "elizabeth city police department") ~ "27909",
        str_detect(AGENCYNAME, "atlantic city police") ~ "8401",
        str_detect(AGENCYNAME, "ventnor city police") ~ "8406",
        str_detect(AGENCYNAME, "brooklawn borough police") ~ "8030",
        str_detect(AGENCYNAME, "woodlynne borough police") ~ "8107",
        str_detect(AGENCYNAME, "north wildwood police department") ~ "8260",
        str_detect(AGENCYNAME, "jersey city police department") ~ "7302",
        str_detect(AGENCYNAME, "lawrence township police") ~ "8648",
        str_detect(AGENCYNAME, "netcong borough police") ~ "7857",
        str_detect(AGENCYNAME, "franklin borough police") & STATE == "NJ" ~ "7416",
        str_detect(AGENCYNAME, "silver city police department") ~ "88061",
        str_detect(AGENCYNAME, "sands point village police department") ~ "11050",
        str_detect(AGENCYNAME, "town of clarkstown police department") ~ "10954",
        str_detect(AGENCYNAME, "bronxville village police department") ~ "10708",
        str_detect(AGENCYNAME, "north kingsville police department") & STATE == "OH" ~ "44048",
        str_detect(AGENCYNAME, "roaming shores police department") ~ "44084",
        str_detect(AGENCYNAME, "brooklyn heights village police department") ~ "44131",
        str_detect(AGENCYNAME, "north randall police department") ~ "44128",
        str_detect(AGENCYNAME, "elk city police department") ~ "73644",
        str_detect(AGENCYNAME, "oklahoma city police department") ~ "73102",
        str_detect(AGENCYNAME, "oregon city police department") ~ "97045",
        str_detect(AGENCYNAME, "columbia city police department") & STATE == "OR" ~ "97018",
        str_detect(AGENCYNAME, "millvale borough police department") ~ "15209",
        str_detect(AGENCYNAME, "elizabeth borough police department") ~ "15037",
        str_detect(AGENCYNAME, "port vue borough police department") ~ "15133",
        str_detect(AGENCYNAME, "tarentum borough police department") ~ "15084",
        str_detect(AGENCYNAME, "leechburg borough police department") ~ "15656",
        str_detect(AGENCYNAME, "beaver borough police department") ~ "15009",
        str_detect(AGENCYNAME, "kutztown borough police department") ~ "19530",
        str_detect(AGENCYNAME, "canton borough police department") ~ "17724",
        str_detect(AGENCYNAME, "plumstead township police department") ~ "18902",
        str_detect(AGENCYNAME, "parkesburg borough police department") ~ "19365",
        str_detect(AGENCYNAME, "knox borough police department") ~ "16232",
        str_detect(AGENCYNAME, "highspire borough police department") ~ "17034",
        str_detect(AGENCYNAME, "trainer borough police department") ~ "19061",
        str_detect(AGENCYNAME, "greencastle borough police department") ~ "17225",
        str_detect(AGENCYNAME, "brockway borough police department") ~ "15824",
        str_detect(AGENCYNAME, "sykesville borough police department") ~ "15865",
        str_detect(AGENCYNAME, "west lampeter township police department") ~ "17602",
        str_detect(AGENCYNAME, "slatington borough police department") ~ "18080",
        str_detect(AGENCYNAME, "macungie borough police department") ~ "18062",
        str_detect(AGENCYNAME, "ashley borough police department") ~ "18706",
        str_detect(AGENCYNAME, "rockledge borough police department") ~ "19046",
        str_detect(AGENCYNAME, "royersford borough police department") ~ "19468",
        str_detect(AGENCYNAME, "tatamy borough police department") ~ "18085",
        str_detect(AGENCYNAME, "walnutport borough police department") ~ "18088",
        str_detect(AGENCYNAME, "mifflinburg borough police department") ~ "17844",
        str_detect(AGENCYNAME, "ligonier borough police department") ~ "15658",
        str_detect(AGENCYNAME, "delmont borough police department") ~ "15626",
        str_detect(AGENCYNAME, "meshoppen borough police department") ~ "18630",
        str_detect(AGENCYNAME, "saint matthews police department") ~ "29135",
        str_detect(AGENCYNAME, "eagle butte police department") ~ "57625",
        str_detect(AGENCYNAME, "rapid city police department") ~ "57701",
        str_detect(AGENCYNAME, "clarksburg police department") ~ "26301",
        str_detect(AGENCYNAME, "mountain city police department") ~ "37683",
        str_detect(AGENCYNAME, "kimball police department") ~ "24853",
        str_detect(AGENCYNAME, "johnson city police department") ~ "37601",
        str_detect(AGENCYNAME, "palm valley police department") ~ "78552",
        str_detect(AGENCYNAME, "argyle police department") ~ "76226",
        str_detect(AGENCYNAME, "northlake police department") ~ "76247",
        str_detect(AGENCYNAME, "missouri city police department") ~ "77459",
        str_detect(AGENCYNAME, "league city police department") ~ "77573",
        str_detect(AGENCYNAME, "bayou vista police department") ~ "77563",
        str_detect(AGENCYNAME, "seven points police department") ~ "75143",
        str_detect(AGENCYNAME, "willow park police department") ~ "76087",
        str_detect(AGENCYNAME, "lakeside police department") ~ "76108",
        str_detect(AGENCYNAME, "cedar city police department") ~ "84720",
        str_detect(AGENCYNAME, "salt lake city police department") ~ "84101",
        str_detect(AGENCYNAME, "dumfries police department") ~ "22026",
        str_detect(AGENCYNAME, "weber city police department") ~ "24290",
        str_detect(AGENCYNAME, "weathersfield police department") ~ "44420",
        str_detect(AGENCYNAME, "royal city police department") ~ "99357",
        str_detect(AGENCYNAME, "clyde hill police department") ~ "98004",
        str_detect(AGENCYNAME, "ruston police department") ~ "98407",
        str_detect(AGENCYNAME, "river hills police department") ~ "53217",
        str_detect(AGENCYNAME, "west milwaukee police department") ~ "53215",
        str_detect(AGENCYNAME, "saint marys police department") ~ "15857",
        str_detect(AGENCYNAME, "lincoln county sheriff's office") ~ "69101",
        str_detect(AGENCYNAME, "san mateo county sheriff's office") ~ "94063",
        str_detect(AGENCYNAME, "columbia county sheriff's office") ~ "32055",
        str_detect(AGENCYNAME, "sac county sheriff's office") ~ "95814",
        str_detect(AGENCYNAME, "stanton county sheriff's department") ~ "68779",
        str_detect(AGENCYNAME, "jefferson county sheriff's office") & STATE == "KY" ~ "40202",
        str_detect(AGENCYNAME, "harford county sheriff's office") ~ "21015",
        str_detect(AGENCYNAME, "otoe county sheriff's office") ~ "68410",
        str_detect(AGENCYNAME, "new hanover county sheriff's office") ~ "28401",
        str_detect(AGENCYNAME, "swain county sheriff's office") ~ "28713",
        str_detect(AGENCYNAME, "barnes county sheriff's office") ~ "58072",
        str_detect(AGENCYNAME, "hudson county sheriff's office") & STATE == "NJ" ~ "7302",
        str_detect(AGENCYNAME, "douglas county sheriff's office") ~ "80109",
        str_detect(AGENCYNAME, "rockland county sheriff's office") ~ "10977",
        str_detect(AGENCYNAME, "clackamas county sheriff's office") ~ "97045",
        str_detect(AGENCYNAME, "campbell county sheriff's office") ~ "41031",
        str_detect(AGENCYNAME, "cheatham county sheriff's office") ~ "37015",
        str_detect(AGENCYNAME, "cameron county sheriff's office") ~ "78520",
        str_detect(AGENCYNAME, "karnes county sheriff's office") ~ "78118",
        str_detect(AGENCYNAME, "starr county sheriff's office") ~ "78582",
        str_detect(AGENCYNAME, "spotsylvania county sheriff's office") ~ "22553",
        str_detect(AGENCYNAME, "stafford county sheriff's office") ~ "22554",
    TRUE ~ ZIP),
    is_city = ifelse(!is.na(County), 0, 1),
    county_state = ifelse(!is.na(County), paste(County, STATE, sep= "_"), NA),
    city_state = ifelse(is.na(County), paste(City, STATE, sep= "_"), NA),
    location = ifelse(is_city == 1, city_state, county_state),
    ZIP = ifelse(substr(ZIP, 1, 1) == "0", substr(ZIP, 2, nchar(ZIP)), ZIP),
    zip = ZIP
    ) %>%
  select(AGENCYNAME, location, OPBUDGET_2019, OPBUDGET, is_city, zip, where(~ all(!is.na(.))))

budgets_2021 <- read_csv("data/opbudgets_2021_2022.csv")

police_df <- police_df %>%
  left_join(budgets_2021, by = c("AGENCYNAME", "STATE"))

police_df <- police_df %>%
  select(-opbudget2019, -source)

```

```{r combine_dfs, eval = FALSE}
full_df <- police_df %>%
  left_join(blm, by = c("location", "is_city")) %>%
  left_join(demographics, by = c("location", "is_city")) %>%
  left_join(zips_pol_ideo_by_num, by = "zip") %>%
  left_join(police_killings, by = c("location")) %>%
  mutate(has_police_killing = ifelse(is.na(has_police_killing), 0, is.numeric(has_police_killing)),
         violent_protest = ifelse(is.na(violent_protest), 0, violent_protest),
         peaceful_protest = ifelse(is.na(peaceful_protest), 0, peaceful_protest))

full_df_processed <- full_df %>%
  select(-AGENCYNAME, -SUBMIT_DATE, -ORI9, -CITY, -STATE, -ZIP, 
         -City, -contains("OTH"), -location, -city, -is_city.y) %>% #remove cols that won't work with MissForest
  mutate(zip = as.numeric(zip),
         across(where(is.character), as.factor)) %>%
  rename(is_city = is_city.x)

full_df_imputed <- missForest(full_df_processed,
                              replace = TRUE)

OOB_error <- full_df_imputed$OOBerror #0.78

final_df <- full_df_imputed$ximp

full_df_processed <- as.data.frame(full_df_processed)

final_df_true <- cbind(full_df$AGENCYNAME, full_df$City, full_df$STATE, final_df)

save(final_df_true, file = "full_data.RData")
```

```{r}
ntree_vals <- c(50, 100, 150)  # Number of trees in the forest
maxiter_vals <- c(5, 10, 15)   # Maximum number of iterations
mtry_vals <- c(2, 3)  

# Initialize variables to track best parameters and OOB error
best_params <- NULL
min_oob_error <- Inf

# Loop over parameter combinations
for (ntree in ntree_vals) {
  for (maxiter in maxiter_vals) {
    for (mtry in mtry_vals) {
      # Run missForest with current parameters
      imputed_data <- missForest(full_df_processed, 
                                 maxiter = maxiter,
                                 ntree = ntree,
                                 mtry = mtry,
                                 replace = TRUE)
      
      # Extract OOB error
      OOB_error <- imputed_data$OOBerror[1]
      
      # Check if current OOB error is lower than minimum found so far
      if (OOB_error < min_oob_error) {
        min_oob_error <- OOB_error
        best_params <- list(ntree = ntree, maxiter = maxiter, mtry = mtry)
      }
    }
  }
}

# Print best parameters and corresponding OOB error
cat("Best Parameters:\n")
print(best_params)
cat("Minimum OOB Error:", min_oob_error, "\n")
```


```{r load_full_data}
load("full_data.RData")

```

# Showing pre-matched data

```{r show_pre_matched_stats_peaceful}
# Initialize an empty data frame to store results
result_table <- data.frame(
  Variable = character(),
  Control_Mean = numeric(),
  Treatment_Mean = numeric(),
  Control_SD = numeric(),
  Treatment_SD = numeric(),
  stringsAsFactors = FALSE
)

# List of variables to analyze
variables <- c("mrp_ideology", "percent_female", "perc_age_0_17", "perc_age_18_34",
               "perc_age_35_59", "perc_age_60_74", "perc_75_up", "perc_black",
               "perc_white", "perc_hispanic", "perc_less_hs",
               "perc_associates", "perc_bachelors", "perc_graduate_professional",
               "perc_not_in_labor_force", "median_hh_income", "has_police_killing")

variable_names <- c(
  "mrp_ideology" = "Ideology",
  "percent_female" = "Percent Female",
  "perc_age_0_17" = "Percent Age 0-17",
  "perc_age_18_34" = "Percent Age 18-34",
  "perc_age_35_59" = "Percent Age 35-59",
  "perc_age_60_74" = "Percent Age 60-74",
  "perc_75_up" = "Percent Age 75+",
  "perc_black" = "Percent Black",
  "perc_white" = "Percent White",
  "perc_hispanic" = "Percent Hispanic",
  "perc_less_hs" = "Percent Less Than High School",
  "perc_associates" = "Percent Associates",
  "perc_bachelors" = "Percent Bachelors",
  "perc_graduate_professional" = "Percent Graduate/Professional",
  "perc_not_in_labor_force" = "Percent Not in Labor Force",
  "median_hh_income" = "Median Household Income",
  "has_police_killing" = "Has Police Killing"
)

# Loop over each variable
for (variable in variables) {
  if (variable == "has_police_killing") {
    # For binary variables, calculate proportions
    prop_treatment <- mean(final_df_true[[variable]][final_df_true$peaceful_protest == 1], na.rm = TRUE)
    prop_control <- mean(final_df_true[[variable]][final_df_true$peaceful_protest == 0], na.rm = TRUE)
    
    # Create a new row for the result_table for binary variable
    new_row <- data.frame(
      Variable = variable_names[[variable]],  # Use the new descriptive name
      Control_Mean = NA,  # Not applicable
      Treatment_Mean = NA, # Not applicable
      Control_SD = NA, # Not applicable
      Treatment_SD = NA, # Not applicable
      Control_Percentage = as.numeric(prop_control),
      Treatment_Percentage = as.numeric(prop_treatment),
      stringsAsFactors = FALSE
    )
  } else {
    # Perform t-test and compute means and standard deviations for continuous variables
    test <- t.test(final_df_true[[variable]][final_df_true$peaceful_protest == 1], 
                   final_df_true[[variable]][final_df_true$peaceful_protest == 0])
    mean_treatment <- mean(final_df_true[[variable]][final_df_true$peaceful_protest == 1], na.rm = TRUE)
    mean_control <- mean(final_df_true[[variable]][final_df_true$peaceful_protest == 0], na.rm = TRUE)
    sd_treatment <- sd(final_df_true[[variable]][final_df_true$peaceful_protest == 1], na.rm = TRUE)
    sd_control <- sd(final_df_true[[variable]][final_df_true$peaceful_protest == 0], na.rm = TRUE)
    
    # Create a new row for the result_table
    new_row <- data.frame(
      Variable = variable_names[[variable]],  # Use the new descriptive name
      Control_Mean = as.numeric(mean_control),
      Treatment_Mean = as.numeric(mean_treatment),
      Control_SD = as.numeric(sd_control),
      Treatment_SD = as.numeric(sd_treatment),
      Control_Percentage = NA, # Not applicable
      Treatment_Percentage = NA, # Not applicable
      stringsAsFactors = FALSE
    )
  }
  
  # Append the new row to result_table
  result_table <- bind_rows(result_table, new_row)
}

table1 <- result_table %>%
  mutate(
    Control_Mean = format(Control_Mean, scientific = FALSE, digits = 4),
    Treatment_Mean = format(Treatment_Mean, scientific = FALSE, digits = 4),
    Control_SD = format(Control_SD, scientific = FALSE, digits = 4),
    Treatment_SD = format(Treatment_SD, scientific = FALSE, digits = 4)
  )  %>%
  rename(`Control Mean` = Control_Mean,
         `Treatment Mean` = Treatment_Mean,
         `Control Std Dev` = Control_SD,
         `Treatment Std Dev` = Treatment_SD,
         `Control Percentage` = Control_Percentage,
         `Treatment Percentage` = Treatment_Percentage)

save(table1, file = "table1.rda")
```

```{r show_pre_matched_stats_violent}
# Initialize an empty data frame to store results
result_table <- data.frame(
  Variable = character(),
  Control_Mean = numeric(),
  Treatment_Mean = numeric(),
  Control_SD = numeric(),
  Treatment_SD = numeric(),
  stringsAsFactors = FALSE
)

# List of variables to analyze
variables <- c("mrp_ideology", "percent_female", "perc_age_0_17", "perc_age_18_34",
               "perc_age_35_59", "perc_age_60_74", "perc_75_up", "perc_black",
               "perc_white", "perc_hispanic", "perc_less_hs",
               "perc_associates", "perc_bachelors", "perc_graduate_professional",
               "perc_not_in_labor_force", "median_hh_income", "has_police_killing")

variable_names <- c(
  "mrp_ideology" = "Ideology",
  "percent_female" = "Percent Female",
  "perc_age_0_17" = "Percent Age 0-17",
  "perc_age_18_34" = "Percent Age 18-34",
  "perc_age_35_59" = "Percent Age 35-59",
  "perc_age_60_74" = "Percent Age 60-74",
  "perc_75_up" = "Percent Age 75+",
  "perc_black" = "Percent Black",
  "perc_white" = "Percent White",
  "perc_hispanic" = "Percent Hispanic",
  "perc_less_hs" = "Percent Less Than High School",
  "perc_associates" = "Percent Associates",
  "perc_bachelors" = "Percent Bachelors",
  "perc_graduate_professional" = "Percent Graduate/Professional",
  "perc_not_in_labor_force" = "Percent Not in Labor Force",
  "median_hh_income" = "Median Household Income",
  "has_police_killing" = "Has Police Killing"
)

# Loop over each variable
for (variable in variables) {
  if (variable == "has_police_killing") {
    # For binary variables, calculate proportions
    prop_treatment <- mean(final_df_true[[variable]][final_df_true$violent_protest == 1], na.rm = TRUE)
    prop_control <- mean(final_df_true[[variable]][final_df_true$violent_protest == 0], na.rm = TRUE)
    
    # Create a new row for the result_table for binary variable
    new_row <- data.frame(
      Variable = variable_names[[variable]],  # Use the new descriptive name
      Control_Mean = NA,  # Not applicable
      Treatment_Mean = NA, # Not applicable
      Control_SD = NA, # Not applicable
      Treatment_SD = NA, # Not applicable
      Control_Percentage = as.numeric(prop_control),
      Treatment_Percentage = as.numeric(prop_treatment),
      stringsAsFactors = FALSE
    )
  } else {
    # Perform t-test and compute means and standard deviations for continuous variables
    test <- t.test(final_df_true[[variable]][final_df_true$violent_protest == 1], 
                   final_df_true[[variable]][final_df_true$violent_protest == 0])
    mean_treatment <- mean(final_df_true[[variable]][final_df_true$violent_protest == 1], na.rm = TRUE)
    mean_control <- mean(final_df_true[[variable]][final_df_true$violent_protest == 0], na.rm = TRUE)
    sd_treatment <- sd(final_df_true[[variable]][final_df_true$violent_protest == 1], na.rm = TRUE)
    sd_control <- sd(final_df_true[[variable]][final_df_true$violent_protest == 0], na.rm = TRUE)
    
    # Create a new row for the result_table
    new_row <- data.frame(
      Variable = variable_names[[variable]],  # Use the new descriptive name
      Control_Mean = as.numeric(mean_control),
      Treatment_Mean = as.numeric(mean_treatment),
      Control_SD = as.numeric(sd_control),
      Treatment_SD = as.numeric(sd_treatment),
      Control_Percentage = NA, # Not applicable
      Treatment_Percentage = NA, # Not applicable
      stringsAsFactors = FALSE
    )
  }
  
  # Append the new row to result_table
  result_table <- bind_rows(result_table, new_row)
}

table2 <- result_table %>%
  mutate(
    Control_Mean = format(Control_Mean, scientific = FALSE, digits = 4),
    Treatment_Mean = format(Treatment_Mean, scientific = FALSE, digits = 4),
    Control_SD = format(Control_SD, scientific = FALSE, digits = 4),
    Treatment_SD = format(Treatment_SD, scientific = FALSE, digits = 4)
  )  %>%
  rename(`Control Mean` = Control_Mean,
         `Treatment Mean` = Treatment_Mean,
         `Control Std Dev` = Control_SD,
         `Treatment Std Dev` = Treatment_SD,
         `Control Percentage` = Control_Percentage,
         `Treatment Percentage` = Treatment_Percentage)

save(table2, file = "table2.rda")
```


### Normalize Data
```{r fix_skewness}
skewed_data <- final_df_true %>%
  select(mrp_ideology, percent_female, perc_age_0_17, 
         perc_age_18_34, perc_age_35_59, perc_age_60_74, perc_75_up,
         perc_black, perc_white, perc_hispanic, perc_less_hs,
         perc_associates, perc_bachelors, perc_graduate_professional,
         perc_not_in_labor_force, median_hh_income)

# Transform skewed data
normalized_data <- transform_skewed_data(skewed_data)

# Function to create histogram using ggplot
create_histogram <- function(data, var_name) { #add print to show skewness plots
  hist <- ggplot(data, aes_string(x = var_name)) +
    geom_histogram(binwidth = 0.5, fill = "blue", color = "black", alpha = 0.7) +
    labs(title = paste("Histogram of", var_name), x = var_name, y = "Frequency") +
    theme_minimal()
  
  print(hist)
}

# Function to create Q-Q plot using ggplot
create_qqplot <- function(data, var_name) { #add print to show skewness plots
  qqplot<- ggplot(data, aes_string(sample = var_name)) +
    stat_qq() +
    stat_qq_line(col = "red") +
    labs(title = paste("Q-Q Plot of", var_name), x = "Theoretical Quantiles", y = "Sample Quantiles") +
    theme_minimal()
  
  print(hist)
}

for (var_name in colnames(normalized_data)) {
  create_histogram(normalized_data, var_name)
  create_qqplot(normalized_data, var_name)
}

final_df_true <- as.data.frame(final_df_true)
normalized_data <- as.data.frame(normalized_data)

# Merge county_state column from full_protest_data with normalized_test
normalized_df <- cbind(agency_name = final_df_true$`full_df$AGENCYNAME`, 
                       city = final_df_true$`full_df$City`,
                       state = final_df_true$`full_df$STATE`,
                       opbudget2019 = final_df_true$OPBUDGET_2019,
                       opbudget = final_df_true$oppudget_2021_2022,
                       is_city = final_df_true$is_city,
                       has_police_killing = final_df_true$has_police_killing,
                       violent_protest = final_df_true$violent_protest,
                       peaceful_protest = final_df_true$peaceful_protest,
                       normalized_data)

save(normalized_df, file = "normalized_data.RData")
  
```

```{r load_normalized_data}
load("normalized_data.RData")
```

### DID Pre-Matching

```{r peaceful_pre}
outcome_vars_pre <- normalized_df %>%
  select(agency_name, opbudget2019, peaceful_protest) %>%
  mutate(time = 0) %>%
  rename(opbudget = opbudget2019)

outcome_vars_post <- normalized_df %>%
  select(agency_name, opbudget, peaceful_protest) %>%
  mutate(time = 1)

diff_in_diff_df <- rbind(outcome_vars_pre, outcome_vars_post)

diff_diff_output <- lm(opbudget ~ peaceful_protest*time, data = diff_in_diff_df)

pre_peaceful_sum <- summary(diff_diff_output)

# Extract the coefficients, standard errors, t-values, and p-values
coefficients <- pre_peaceful_sum$coefficients

# Convert to a data frame
table3 <- data.frame(
  Variable = rownames(coefficients),
  Estimate = coefficients[, "Estimate"],
  Std_Error = coefficients[, "Std. Error"],
  t_value = coefficients[, "t value"],
  P_Value = coefficients[, "Pr(>|t|)"]
)

save(table3, file = "table3.rda")
```

```{r violent_pre}
outcome_vars_pre <- normalized_df %>%
  select(agency_name, opbudget2019, violent_protest) %>%
  mutate(time = 0) %>%
  rename(opbudget = opbudget2019)

outcome_vars_post <- normalized_df %>%
  select(agency_name, opbudget, violent_protest) %>%
  mutate(time = 1)

diff_in_diff_df <- rbind(outcome_vars_pre, outcome_vars_post)

diff_diff_output <- lm(opbudget ~ violent_protest*time, data = diff_in_diff_df)

pre_violent_sum <- summary(diff_diff_output)

# Extract the coefficients, standard errors, t-values, and p-values
coefficients <- pre_violent_sum$coefficients

# Convert to a data frame
table4 <- data.frame(
  Variable = rownames(coefficients),
  Estimate = coefficients[, "Estimate"],
  Std_Error = coefficients[, "Std. Error"],
  t_value = coefficients[, "t value"],
  P_Value = coefficients[, "Pr(>|t|)"]
)

save(table4, file = "table4.rda")
```

## Propensity Scores

I created propensity scores using County Demographics

```{r peaceful_protests_pscores, fig.height = 7, fig.width = 15}
peaceful_protests <- normalized_df %>%
  select(-violent_protest)

peaceful_protests_pscores <- glm(peaceful_protest ~ mrp_ideology + percent_female +
                                perc_age_0_17 + perc_age_18_34 + perc_age_35_59 + 
                                perc_age_60_74 + perc_75_up + perc_black + 
                                perc_white + perc_hispanic +
                                perc_less_hs + perc_associates + perc_bachelors + 
                                perc_graduate_professional + perc_not_in_labor_force + 
                                median_hh_income + has_police_killing + is_city,
                              data = peaceful_protests,
                              family = binomial(link = "logit"))

peaceful_protests$p_score <- predict(peaceful_protests_pscores,
                                             newdata = peaceful_protests,
                                             type = "response")

plot_peaceful_protests <- ggplot(peaceful_protests) + 
  aes(x = p_score, fill = factor(peaceful_protest), color = factor(peaceful_protest)) + 
  geom_density(alpha = 0.5) +
  xlab("P-Score") +
  ylab("Density") +
  labs(fill = "peaceful_protest", color = "peaceful_protest",
       title = "Propensity Scores: Peaceful Protest: County Demographics") + 
  theme_minimal()

```

```{r violent_protests_pscores, fig.height = 7, fig.width = 15}
violent_protests <- normalized_df %>%
  select(-peaceful_protest)

violent_protests_pscores <- glm(violent_protest ~ mrp_ideology + percent_female +
                                perc_age_0_17 + perc_age_18_34 + perc_age_35_59 + 
                                perc_age_60_74 + perc_75_up + perc_black + 
                                perc_white + perc_hispanic +
                                perc_less_hs + perc_associates + perc_bachelors + 
                                perc_graduate_professional + perc_not_in_labor_force + 
                                median_hh_income + has_police_killing + is_city,
                              data = violent_protests,
                              family = binomial(link = "logit"))

violent_protests$p_score <- predict(violent_protests_pscores,
                                             newdata = violent_protests,
                                             type = "response")

plot_violent_protests <- ggplot(violent_protests) + 
  aes(x = p_score, fill = factor(violent_protest), color = factor(violent_protest)) + 
  geom_density(alpha = 0.5) +
  xlab("P-Score") +
  ylab("Density") +
  labs(fill = "violent_protest", color = "violent_protest",
       title = "Propensity Scores: Violent Protest: County Demographics") + 
  theme_minimal()

grid.arrange(plot_peaceful_protests, plot_violent_protests, nrow = 1)
```

<br/ >

## Matching

```{r conduct_match_it, echo = TRUE}
m_out_peaceful <- MatchIt::matchit(peaceful_protest~p_score, 
                          data = peaceful_protests,
                          method = "genetic",
                          ratio = 3,
                          replace = T,
                          distance = "mahalanobis")

m_out_violent <- MatchIt::matchit(violent_protest~p_score, 
                          data = violent_protests,
                          method = "genetic",
                          ratio = 3,
                          replace = T,
                          distance = "mahalanobis")

```

```{r show_treat_control_groups}
m_data_peaceful <- MatchIt::match.data(m_out_peaceful)
m_data_violent <- MatchIt::match.data(m_out_violent)

counts <- table(m_data_peaceful$peaceful_protest)
num_control <- counts[as.character(0)]  # Number of control units
num_treatment <- counts[as.character(1)]

cat("The peaceful matched data set has", dim(m_data_peaceful)[1], "counties.", num_control, "are in control",
    num_treatment, "are in treatment.", "The original dataset had", nrow(normalized_df), "counties.")

counts <- table(m_data_violent$violent_protest)
num_control <- counts[as.character(0)]  # Number of control units
num_treatment <- counts[as.character(1)]

cat("The violent matched data set has", dim(m_data_violent)[1], "counties.", num_control, "are in control",
    num_treatment, "are in treatment.", "The original dataset had", nrow(normalized_df), "counties.")

```


```{r show_group_metrics}
# Initialize an empty data frame to store results
result_table <- data.frame(
  Variable = character(),
  Control_Mean = numeric(),
  Treatment_Mean = numeric(),
  Control_SD = numeric(),
  Treatment_SD = numeric(),
  stringsAsFactors = FALSE
)

# List of variables to analyze
variables <- c("mrp_ideology", "percent_female", "perc_age_0_17", "perc_age_18_34",
               "perc_age_35_59", "perc_age_60_74", "perc_75_up", "perc_black",
               "perc_white", "perc_hispanic", "perc_less_hs",
               "perc_associates", "perc_bachelors", "perc_graduate_professional",
               "perc_not_in_labor_force", "median_hh_income", "has_police_killing")

variable_names <- c(
  "mrp_ideology" = "Ideology",
  "percent_female" = "Percent Female",
  "perc_age_0_17" = "Percent Age 0-17",
  "perc_age_18_34" = "Percent Age 18-34",
  "perc_age_35_59" = "Percent Age 35-59",
  "perc_age_60_74" = "Percent Age 60-74",
  "perc_75_up" = "Percent Age 75+",
  "perc_black" = "Percent Black",
  "perc_white" = "Percent White",
  "perc_hispanic" = "Percent Hispanic",
  "perc_less_hs" = "Percent Less Than High School",
  "perc_associates" = "Percent Associates",
  "perc_bachelors" = "Percent Bachelors",
  "perc_graduate_professional" = "Percent Graduate/Professional",
  "perc_not_in_labor_force" = "Percent Not in Labor Force",
  "median_hh_income" = "Median Household Income",
  "has_police_killing" = "Has Police Killing"
)

# Loop over each variable
for (variable in variables) {
  if (variable == "has_police_killing") {
    # For binary variables, calculate proportions
    prop_treatment <- mean(m_data_peaceful[[variable]][m_data_peaceful$peaceful_protest == 1], na.rm = TRUE)
    prop_control <- mean(m_data_peaceful[[variable]][m_data_peaceful$peaceful_protest == 0], na.rm = TRUE)
    
    # Create a new row for the result_table for binary variable
    new_row <- data.frame(
      Variable = variable_names[[variable]],  # Use the new descriptive name
      Control_Mean = NA,  # Not applicable
      Treatment_Mean = NA, # Not applicable
      Control_SD = NA, # Not applicable
      Treatment_SD = NA, # Not applicable
      Control_Percentage = as.numeric(prop_control),
      Treatment_Percentage = as.numeric(prop_treatment),
      stringsAsFactors = FALSE
    )
  } else {
    # Perform t-test and compute means and standard deviations for continuous variables
    test <- t.test(m_data_peaceful[[variable]][m_data_peaceful$peaceful_protest == 1], 
                   m_data_peaceful[[variable]][m_data_peaceful$peaceful_protest == 0])
    mean_treatment <- mean(m_data_peaceful[[variable]][m_data_peaceful$peaceful_protest == 1], na.rm = TRUE)
    mean_control <- mean(m_data_peaceful[[variable]][m_data_peaceful$peaceful_protest == 0], na.rm = TRUE)
    sd_treatment <- sd(m_data_peaceful[[variable]][m_data_peaceful$peaceful_protest == 1], na.rm = TRUE)
    sd_control <- sd(m_data_peaceful[[variable]][m_data_peaceful$peaceful_protest == 0], na.rm = TRUE)
    
    # Create a new row for the result_table
    new_row <- data.frame(
      Variable = variable_names[[variable]],  # Use the new descriptive name
      Control_Mean = as.numeric(mean_control),
      Treatment_Mean = as.numeric(mean_treatment),
      Control_SD = as.numeric(sd_control),
      Treatment_SD = as.numeric(sd_treatment),
      Control_Percentage = NA, # Not applicable
      Treatment_Percentage = NA, # Not applicable
      stringsAsFactors = FALSE
    )
  }
  
  # Append the new row to result_table
  result_table <- bind_rows(result_table, new_row)
}

table5 <- result_table %>%
  mutate(
    Control_Mean = format(Control_Mean, scientific = FALSE, digits = 4),
    Treatment_Mean = format(Treatment_Mean, scientific = FALSE, digits = 4),
    Control_SD = format(Control_SD, scientific = FALSE, digits = 4),
    Treatment_SD = format(Treatment_SD, scientific = FALSE, digits = 4)
  )  %>%
  rename(`Control Mean` = Control_Mean,
         `Treatment Mean` = Treatment_Mean,
         `Control Std Dev` = Control_SD,
         `Treatment Std Dev` = Treatment_SD,
         `Control Percentage` = Control_Percentage,
         `Treatment Percentage` = Treatment_Percentage)

save(table5, file = "table5.rda")
```

```{r show_group_metrics}
# Initialize an empty data frame to store results
result_table <- data.frame(
  Variable = character(),
  Control_Mean = numeric(),
  Treatment_Mean = numeric(),
  Control_SD = numeric(),
  Treatment_SD = numeric(),
  stringsAsFactors = FALSE
)

# List of variables to analyze
variables <- c("mrp_ideology", "percent_female", "perc_age_0_17", "perc_age_18_34",
               "perc_age_35_59", "perc_age_60_74", "perc_75_up", "perc_black",
               "perc_white", "perc_hispanic", "perc_less_hs",
               "perc_associates", "perc_bachelors", "perc_graduate_professional",
               "perc_not_in_labor_force", "median_hh_income", "has_police_killing")

variable_names <- c(
  "mrp_ideology" = "Ideology",
  "percent_female" = "Percent Female",
  "perc_age_0_17" = "Percent Age 0-17",
  "perc_age_18_34" = "Percent Age 18-34",
  "perc_age_35_59" = "Percent Age 35-59",
  "perc_age_60_74" = "Percent Age 60-74",
  "perc_75_up" = "Percent Age 75+",
  "perc_black" = "Percent Black",
  "perc_white" = "Percent White",
  "perc_hispanic" = "Percent Hispanic",
  "perc_less_hs" = "Percent Less Than High School",
  "perc_associates" = "Percent Associates",
  "perc_bachelors" = "Percent Bachelors",
  "perc_graduate_professional" = "Percent Graduate/Professional",
  "perc_not_in_labor_force" = "Percent Not in Labor Force",
  "median_hh_income" = "Median Household Income",
  "has_police_killing" = "Has Police Killing"
)

# Loop over each variable
for (variable in variables) {
  if (variable == "has_police_killing") {
    # For binary variables, calculate proportions
    prop_treatment <- mean(m_data_violent[[variable]][m_data_violent$violent_protest == 1], na.rm = TRUE)
    prop_control <- mean(m_data_violent[[variable]][m_data_violent$violent_protest == 0], na.rm = TRUE)
    
    # Create a new row for the result_table for binary variable
    new_row <- data.frame(
      Variable = variable_names[[variable]],  # Use the new descriptive name
      Control_Mean = NA,  # Not applicable
      Treatment_Mean = NA, # Not applicable
      Control_SD = NA, # Not applicable
      Treatment_SD = NA, # Not applicable
      Control_Percentage = as.numeric(prop_control),
      Treatment_Percentage = as.numeric(prop_treatment),
      stringsAsFactors = FALSE
    )
  } else {
    # Perform t-test and compute means and standard deviations for continuous variables
    test <- t.test(m_data_violent[[variable]][m_data_violent$violent_protest == 1], 
                   m_data_violent[[variable]][m_data_violent$violent_protest == 0])
    mean_treatment <- mean(m_data_violent[[variable]][m_data_peaceful$violent_protest == 1], na.rm = TRUE)
    mean_control <- mean(m_data_violent[[variable]][m_data_peaceful$violent_protest == 0], na.rm = TRUE)
    sd_treatment <- sd(m_data_violent[[variable]][m_data_peaceful$violent_protest == 1], na.rm = TRUE)
    sd_control <- sd(m_data_violent[[variable]][m_data_peaceful$violent_protest == 0], na.rm = TRUE)
    
    # Create a new row for the result_table
    new_row <- data.frame(
      Variable = variable_names[[variable]],  # Use the new descriptive name
      Control_Mean = as.numeric(mean_control),
      Treatment_Mean = as.numeric(mean_treatment),
      Control_SD = as.numeric(sd_control),
      Treatment_SD = as.numeric(sd_treatment),
      Control_Percentage = NA, # Not applicable
      Treatment_Percentage = NA, # Not applicable
      stringsAsFactors = FALSE
    )
  }
  
  # Append the new row to result_table
  result_table <- bind_rows(result_table, new_row)
}

table6 <- result_table %>%
  mutate(
    Control_Mean = format(Control_Mean, scientific = FALSE, digits = 4),
    Treatment_Mean = format(Treatment_Mean, scientific = FALSE, digits = 4),
    Control_SD = format(Control_SD, scientific = FALSE, digits = 4),
    Treatment_SD = format(Treatment_SD, scientific = FALSE, digits = 4)
  )  %>%
  rename(`Control Mean` = Control_Mean,
         `Treatment Mean` = Treatment_Mean,
         `Control Std Dev` = Control_SD,
         `Treatment Std Dev` = Treatment_SD,
         `Control Percentage` = Control_Percentage,
         `Treatment Percentage` = Treatment_Percentage)

save(table6, file = "table6.rda")
```

### DID Post Matching

```{r peaceful_post}
outcome_vars_pre <- m_data_peaceful %>%
  select(agency_name, opbudget2019, peaceful_protest) %>%
  mutate(time = 0) %>%
  rename(opbudget = opbudget2019)

outcome_vars_post <- m_data_peaceful %>%
  select(agency_name, opbudget, peaceful_protest) %>%
  mutate(time = 1)

diff_in_diff_peace <- rbind(outcome_vars_pre, outcome_vars_post)

diff_diff_output <- lm(opbudget ~ peaceful_protest*time, data = diff_in_diff_peace)

summary(diff_diff_output)

```

```{r violent_post, echo = TRUE}
outcome_vars_pre <- m_data_violent %>%
  select(agency_name, opbudget2019, violent_protest) %>%
  mutate(time = 0) %>%
  rename(opbudget = opbudget2019)

outcome_vars_post <- m_data_violent %>%
  select(agency_name, opbudget, violent_protest) %>%
  mutate(time = 1)

diff_in_diff_violent <- rbind(outcome_vars_pre, outcome_vars_post)

diff_diff_output <- lm(opbudget ~ violent_protest*time, data = diff_in_diff_violent)

summary(diff_diff_output)

```

#### Parallel Trends

```{r peaceful}
diff_in_diff_peace %>% group_by(peaceful_protest, time) %>%
  summarise(opbudget = mean(opbudget)) %>%
  ggplot() + aes(x = time, y = opbudget, color = factor(peaceful_protest)) +
  geom_point(size = 5) +
  geom_line() +
  geom_line(data = . %>% filter(peaceful_protest == 0), aes(y = opbudget + 10000), color = "grey") + labs(color = "Treated") +
  scale_x_continuous(breaks = c(0 , 1), labels = c("Before", "After")) + theme_minimal() +
  xlab("") +
  ylab("")

```

```{r violent}
diff_in_diff_violent %>% group_by(violent_protest, time) %>%
  summarise(opbudget = mean(opbudget)) %>%
  ggplot() + aes(x = time, y = opbudget, color = factor(violent_protest)) +
  geom_point(size = 5) +
  geom_line() +
  geom_line(data = . %>% filter(violent_protest == 0), aes(y = opbudget + 10000), color = "grey") + labs(color = "Treated") +
  scale_x_continuous(breaks = c(0 , 1), labels = c("Before", "After")) + theme_minimal() +
  xlab("") +
  ylab("")
```


```{r, eval = FALSE}
counties_blm_map <- counties_blm %>%
  ungroup %>%
  select(-county_state)

cities_blm_map <- cities_blm %>%
  ungroup %>%
  select(-city_state)

protest_locations <- rbind(counties_blm_map, cities_blm_map)

protest_locations_processed <- protest_locations %>%
  mutate(event_type = ifelse(violent_protest == 1, "violent_protest",
                      ifelse(peaceful_protest == 1, "peaceful_protest", "no protest")))

tmap_mode("view")

shp <- tigris::states()

# Remove the long archipelago of islands to the northwest of Hawaii to fix scale
shp <- shp  %>% filter(REGION != 9) %>% shift_geometry()

vis <- tm_shape(shp) + 
  tm_borders()

protests <- st_as_sf(protest_locations, coords = c("longitude", "latitude"))

protests_processed <- cbind(protests, protest_locations_processed$event_type)

vis <- vis + tm_shape(protests) +
  tm_bubbles(size=0.05, alpha =0.5)
```

```{r}
library(tidygeocoder)

police_deparment_names <- paste(normalized_df$agency_name, normalized_df$state)

View(normalized_df)

geo_coded_results <- geo(na_1, method = "arcgis", full_results = TRUE)

geo_coded_results_df <- geo_coded_results %>%
  select(address, lat, long)

not_na_2 <- as.data.frame(filter(geo_coded_results_df, !is.na(geo_coded_results_df$lat)))

na_1 <- unlist(na_1)

save(not_na_2, file = "not_na_2.RData")

not_na <- rbind(not_na_1, not_na_2)
```

```{r}
tmap_mode("view")

shp <- tigris::states()

# Remove the long archipelago of islands to the northwest of Hawaii to fix scale
shp <- shp  %>% filter(REGION != 9) %>% shift_geometry()

vis <- tm_shape(shp) + 
  tm_borders()

police_stations <- st_as_sf(not_na, coords = c("long", "lat"))

vis <- vis + tm_shape(police_stations) +
  tm_bubbles(size=0.05, alpha =0.5)
```

```{r}
library(units)

check_proximity <- function(police_station, protests) {
  distances <- st_distance(police_station, protests)
  distances_miles <- set_units(distances, "miles")
  within_radius <- distances_miles <= set_units(5, "miles")
  protest_types <- protests[within_radius, "protest_locations_processed.event_type"]
  
  violent_protest <- any(protest_types$event_type == "violent_protest")
  peaceful_protest <- any(protest_types$event_type == "peaceful_protest")
  
  return(data.frame(
    department_name = police_stations$address,
    peaceful_protest = as.integer(peaceful_protest),
    violent_protest = as.integer(violent_protest)
  ))
}

# Apply the function to each police station
results <- do.call(rbind, lapply(1:nrow(police_stations), function(i) {
  check_proximity(police_stations[i,], protests_processed)
}))

# View the results
print(results)
```

