---
title: "Appendix"
output:
  pdf_document: default
  word_document: default
date: "2024-08-15"
geometry: margin=0.75in
---

```{r setup, include=FALSE}
# Load data into global environment. 
library(finalfit)
library(dplyr)
library(knitr)
library(kableExtra)
load("tables_figures/table1.rda")
load("tables_figures/table2.rda")
load("tables_figures/table3.rda")
load("tables_figures/table4.rda")
load("tables_figures/table5.rda")
load("tables_figures/table6.rda")
load("tables_figures/table7.rda")
load("tables_figures/table8.rda")
load("tables_figures/figure1.rda")
load("tables_figures/figure2.rda")
load("tables_figures/figure3.rda")
load("tables_figures/summary_stats.rda")
load("tables_figures/parallel_peaceful.rda")
load("tables_figures/parallel_violent.rda")
```

## Figure 1 - Normalized RMSE of Successive Imputations: MICE vs missForest

```{r figure1, echo = FALSE, results='asis'}
figure1
```

## Figure 2 - Peaceful Analysis: Comparison of Means for Removed vs. Not Removed Rows
```{r figure2, echo = FALSE, results='asis'}
figure2
```

## Figure 3 - Violent Analysis: Comparison of Means for Removed vs. Not Removed Rows
```{r figrue3, echo = FALSE, results='asis'}
figure3
```

\newpage

## Table 1 - Summary Stats Comparing Imputed vs. Original Data

```{r table1, echo = FALSE, results='asis'}
kable(summary_stats, row.names=FALSE, align=c("l", "l", "r", "r", "r", "r"), booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position"))
```

\newpage

## Table 2 - Peaceful Analysis Parallel Trends
```{r parallel_peaceful, echo = FALSE, results='asis'}
kable(parallel_peaceful, row.names=FALSE, align=c("l", "l", "r", "r", "r", "r"), booktabs=TRUE)
```

## Table 3 - Violent Analysis Parallel Trends
```{r parallel_violent, echo = FALSE, results='asis'}
kable(parallel_violent, row.names=FALSE, align=c("l", "l", "r", "r", "r", "r"), booktabs=TRUE)
```

\newpage

## Table 4 - Peaceful Analysis Pre Matching
```{r table2, echo = FALSE, results='asis'}
kable(table1, row.names=FALSE, align=c("l", "l", "r", "r", "r", "r"), booktabs=TRUE)
```

## Table 5 - Violent Analysis Pre Matching
```{r table3, echo = FALSE, results='asis'}
kable(table2, row.names=FALSE, align=c("l", "l", "r", "r", "r", "r"), booktabs=TRUE)
```

## Table 6 - DID Analysis Pre-Matching Peaceful
```{r table4, echo = FALSE, results='asis'}
kable(table3, row.names=FALSE, align=c("l", "l", "r", "r", "r", "r"),booktabs=TRUE)
```

## Table 7 - DID Analysis Pre-Matching Violent
```{r table5, echo = FALSE, results='asis'}
kable(table4, row.names=FALSE, align=c("l", "l", "r", "r", "r", "r"),booktabs=TRUE)
```

## Table 8 - Peaceful Analysis Post-Matching
```{r table6, echo = FALSE, results='asis'}
kable(table5, row.names=FALSE, align=c("l", "l", "r", "r", "r", "r"),booktabs=TRUE)
```

\newpage

## Table 9 - Violent Analysis Post-Matching
```{r table7, echo = FALSE, results='asis'}
kable(table6, row.names=FALSE, align=c("l", "l", "r", "r", "r", "r"),booktabs=TRUE)
```

## Table 10 - DID Analysis Post-Matching Peaceful
```{r table8, echo = FALSE, results='asis'}
kable(table7, row.names=FALSE, align=c("l", "l", "r", "r", "r", "r"),booktabs=TRUE)
```

## Table 11 - DID Analysis Post-Matching Violent
```{r table9, echo = FALSE, results='asis'}
kable(table8, row.names=FALSE, align=c("l", "l", "r", "r", "r", "r"),booktabs=TRUE)
```