---
title: "Appendix"
output:
  pdf_document: default
  word_document: default
date: "2024-08-15"
geometry: margin=0.75in
---

```{r setup, include=FALSE}
library(finalfit)
library(dplyr)
library(knitr)
library(kableExtra)
load("tables_figures/did_pre_matching_peaceful.rda")
load("tables_figures/did_pre_matching_violent.rda")
load("tables_figures/balance_pre_match_peaceful.rda")
load("tables_figures/balance_pre_match_violent.rda")
load("tables_figures/balance_post_match_peaceful.rda")
load("tables_figures/balance_post_match_violent.rda")
load("tables_figures/did_post_matching_peaceful.rda")
load("tables_figures/did_post_matching_violent.rda")
load("tables_figures/figure1.rda")
load("tables_figures/removed_peaceful.rda")
load("tables_figures/removed_violent.rda")
load("tables_figures/summary_stats.rda")
load("tables_figures/parallel_peaceful.rda")
load("tables_figures/parallel_violent.rda")
```

## Figure 1 - Normalized RMSE of Successive Imputations: MICE vs missForest

```{r figure1, echo = FALSE, results='asis'}
figure1
```

## Figure 2 - Peaceful Analysis: Comparison of Means for Removed vs. Unremoved Rows
```{r removed_peaceful, echo = FALSE, results='asis'}
removed_peaceful
```

## Figure 3 - Violent Analysis: Comparison of Means for Removed vs. Not Removed Rows
```{r removed_violent, echo = FALSE, results='asis'}
removed_violent
```

\newpage

## Table 1 - Parallel Trends Analysis: Peaceful Protests
```{r parallel_peaceful, echo = FALSE, results='asis'}
kable(parallel_peaceful, row.names=FALSE, align=c("l", "l", "r", "r", "r", "r"), booktabs=TRUE)
```

## Table 2 - Parallel Trends Analysis: Violent Protests
```{r parallel_violent, echo = FALSE, results='asis'}
kable(parallel_violent, row.names=FALSE, align=c("l", "l", "r", "r", "r", "r"), booktabs=TRUE)
```

## Table 3 - Summary Statistics: Comparing Imputed vs. Original Data

```{r summary_stats, echo = FALSE, results='asis'}
kable(summary_stats, row.names=FALSE, align=c("l", "l", "r", "r", "r", "r"), booktabs=TRUE) %>%
  kable_styling(latex_options = c("hold_position"))
```

\newpage

## Table 4 - Comparison of Treatment and Control Group: Peacful Protests Pre-Matching
```{r balance_pre_match_peaceful, echo = FALSE, results='asis'}
kable(balance_pre_match_peaceful, row.names=FALSE, align=c("l", "l", "r", "r", "r", "r"), booktabs=TRUE)
```

## Table 5 - Comparison of Treatment and Control Group: Violent Protests Pre-Matching
```{r balance_pre_match_violent, echo = FALSE, results='asis'}
kable(balance_pre_match_violent, row.names=FALSE, align=c("l", "l", "r", "r", "r", "r"), booktabs=TRUE)
```

## Table 6 - DID Analysis with Pre-Matched Data: Peaceful Protests
```{r did_pre_matching_peaceful, echo = FALSE, results='asis'}
kable(did_pre_matching_peaceful, row.names=FALSE, align=c("l", "l", "r", "r", "r", "r"),booktabs=TRUE)
```

## Table 7 - DID Analysis with Pre-Matched Data: Violent Protests
```{r did_pre_matching_violent, echo = FALSE, results='asis'}
kable(did_pre_matching_violent, row.names=FALSE, align=c("l", "l", "r", "r", "r", "r"),booktabs=TRUE)
```

## Table 8 - Comparison of Treatment and Control Group: Peaceful Protests Post-Matching
```{r balance_post_match_peaceful, echo = FALSE, results='asis'}
kable(balance_post_match_peaceful, row.names=FALSE, align=c("l", "l", "r", "r", "r", "r"),booktabs=TRUE)
```

\newpage

## Table 9 - Comparison of Treatment and Control Group: Violent Protests Post-Matching
```{r balance_post_match_violent, echo = FALSE, results='asis'}
kable(balance_post_match_violent, row.names=FALSE, align=c("l", "l", "r", "r", "r", "r"),booktabs=TRUE)
```

## Table 10 - DID Analysis with Post-Matched Data: Peaceful Protests
```{r did_post_matching_peaceful, echo = FALSE, results='asis'}
kable(did_post_matching_peaceful, row.names=FALSE, align=c("l", "l", "r", "r", "r", "r"),booktabs=TRUE)
```

## Table 11 - DID Analysis with Post-Matched Data: Violent Protests
```{r did_post_matching_violent, echo = FALSE, results='asis'}
kable(did_post_matching_violent, row.names=FALSE, align=c("l", "l", "r", "r", "r", "r"),booktabs=TRUE)
```