---
title: "output_tables"
output: pdf_document
date: "2024-07-21"
geometry: margin=0.75in
---

```{r setup, include=FALSE}
# Load data into global environment. 
library(finalfit)
library(dplyr)
library(knitr)
library(kableExtra)
load("table1.rda")
load("table2.rda")
load("table3.rda")
load("table4.rda")
load("table5.rda")
load("table6.rda")
load("table7.rda")
load("table8.rda")
load("figure1.rda")
load("figure2.rda")
load("figure3.rda")
```

## Table 1 - Peaceful Analysis Pre Matching
```{r table1, echo = FALSE, results='asis'}
kable(table1, row.names=FALSE, align=c("l", "l", "r", "r", "r", "r"),
                        booktabs=TRUE)
```

## Table 2 - Violent Analysis Pre Matching
```{r table2, echo = FALSE, results='asis'}
kable(table2, row.names=FALSE, align=c("l", "l", "r", "r", "r", "r"),
                        booktabs=TRUE)
```

## Table 3 - DID Analysis Pre-Matching Peaceful
```{r table3, echo = FALSE, results='asis'}
kable(table3, row.names=FALSE, align=c("l", "l", "r", "r", "r", "r"),
                        booktabs=TRUE)
```

## Table 4 - DID Analysis Pre-Matching Violent
```{r table4, echo = FALSE, results='asis'}
kable(table4, row.names=FALSE, align=c("l", "l", "r", "r", "r", "r"),
                        booktabs=TRUE)
```

## Table 5 - Peaceful Analysis Post-Matching
```{r table5, echo = FALSE, results='asis'}
kable(table5, row.names=FALSE, align=c("l", "l", "r", "r", "r", "r"),
                        booktabs=TRUE)
```

## Table 6 - Violent Analysis Post-Matching
```{r table6, echo = FALSE, results='asis'}
kable(table6, row.names=FALSE, align=c("l", "l", "r", "r", "r", "r"),
                        booktabs=TRUE)
```

## Figure 3: Normalized RMSE of Successive Imputations: MICE vs missForest

```{r}
figure1
```


## Figure 2 - Peaceful Analysis: Comparison of Means for Removed vs. Not Removed Rows
```{r figure1, echo = FALSE, results='asis'}
figure2
```

## Figure 3 - Violent Analysis: Comparison of Means for Removed vs. Not Removed Rows
```{r}
figure3
```

## Table 7 - DID Analysis Post-Matching Peaceful
```{r table7, echo = FALSE, results='asis'}
kable(table7, row.names=FALSE, align=c("l", "l", "r", "r", "r", "r"),
                        booktabs=TRUE)
```

## Table 8 - DID Analysis Post-Matching Violent
```{r table8, echo = FALSE, results='asis'}
kable(table8, row.names=FALSE, align=c("l", "l", "r", "r", "r", "r"),
                        booktabs=TRUE)
```